Simulating dynein's powerstroke using Brownian dynamics

### 2017-05-03 thesis/latex/thesis.tex
Thesis: Add most of Conclusion section.

\section{Conclusion}

\subsection{Next Steps}
\subsubsection{Limitations}

-------------------------------------
Talk about the things we \textit{don't} take into account...motor-motor interaction, 2d information, other ATPase nucleotide state, saying certain mechanochemical steps occur ``fast,'' not taking into account all mechanochemical cycle states, making the coiled coil domain rigid even though it may be springy, 2D model...

Mention the Burgess paper, which says spring constants might change between apo/ADP states.
Also dynein may move helically: Bidirectional helical motility of cytoplasmic dynein around microtubules

Computational limitations: Our project is computational, not experimental. Thus the onus is on us to show that our system is not a humongously over-fit model which just happens to reproduce experimental data, but rather a good physical model of dynein which also replicates data.\\
-------------------------------------

\subsubsection{Improvements to model}

\subsubsection{\textit{Experiments to verify our model}}
Talk about how FRET could be used to verify our model. We have domain distance info over long timescales in our model - this is something we could compare to a FRET experiment exploring the distance between domains in dynein.\\

Other biophysics experiments which could verify our model?\\

Calorimetry could get Gibb's energy of binding if you froze the motor in onebound using vanadium? Maybe...\\

>>>>

\section{Conclusion}
\subsection{Findings}
The most important findings of this work are that a springy hinge model of dynein can take steps of a similar size to real dynein. What's more, it is likely further tweaking of the model will improve the model's behavior to the point of generating backwards and large steps. This would be a very important result which would strongly support the linker-swing/diffusive-step model of dynein stepping and guide further research.\\

Many studies have been done on dynein, resulting in a large body of literature about the motor's behavior and features. Sifting through this information to find what is important for the motor's step is a difficult task. Mutational studies can remove traits of the motor, deducing what traits are necessary for stepping. However, this process is slow, and it can be difficult to remove large traits of the motor while keeping the engineered dynein representative of the natural motor. This is where simulations come in. Minimal features can be put into a physical model, which can then be tested for behavior similar to real dynein. In this study, we created a mathematical model which simplifies the motor to a rigid hinge structure with harmonic spring energies between the hinges. The equilibrium angles change dynamically to reflect structural changes during dynein's mechanochemical cycle. The model was then subjected to Brownian forces and evolved. If the model generates a stepping pattern similar to real dynein, this would demonstrate that dynein can be thought of as a rigid hinged structure. This would mean that many other traits of dynein may not be vital for stepping, such as stalk elasticity \cite{sarlahmodel}, motor-motor interaction \cite{sarlahmodel}, nucleotide state \cite{cianfroccoreview}, nucleotide state of non-AAA1 nuclease sites \cite{cianfroccoreview}, and changing stiffness of the foot domain \cite{burgess-paper}. Thus future research may want to focus more on linker swing and binding interactions, and less on these other traits.\\

Other findings cast doubt on some aspects of the model. The vast preference of the model for $<5nm$ steps suggests that the model may handle binding events unlike real dynein. When binding, the total spring energy of the transition from a onebound to a bothbound state is calculated, then used to calculate the likelihood of transition via a Boltzmann factor. This approach may be overly simple, or take into account the wrong information. It may be that it is necessary to expand the two-state model into a three-state model with a low-microtubule-affinity onebound state immediately after unbinding, to prevent instant rebinding. This state would eventually transition to the high-microtubule-affinity state after some time. If this proves to be necessary to decrease small steps, this would be an interesting result showing that the motor might rely on its low-microtule-affinity ADP-Pi state to prevent early binding.\\

\subsection{Further work}
The goal of studying dynein's mechanochemical cycle is to find an explanation for how it work. That is, to find the necessary and sufficient properties of dynein that cause the cycle to happen. Simulations are only part of the recipe for creating a scientific theory. Simulations are easy to implement and can study phenomena which are difficult to design experiments for. However, when experimental data is available, it is generally more reliable than a simulation of the same system. This is because a simulation is only as good as the strength of correspondence between the mathematical model and the system it represents. With dynein, this correspondence can be hard to achieve because the protein is complicated. The model predicts, according to the laws of physics for small objects, how a small machine composed of springy hinges would behave in an aqueous environment. This machine can be made the same size and general shape as dynein, and its conformational angles can be made the same as dynein's, and its state transitions can happen in the same way dynein's do. However, it is never possible to say that this machine ``is'' dynein or represents how dynein actually behaves. Thus, it is only possible to say that the simulation provides sufficient criteria for dynein stepping, not necessary criteria. The simulation shows that the linker-swing/diffusive-step model is sufficient for motion, but it cannot show that this is needed for dynein's walk.\\

To more strongly support the linker-swing/diffusive step model of dynein motion, more experiments should be done. Demonstrating that dynein requires flexible domain connections in order to take such broad steps would be one powerful experiment. Mutating the foot and tail domains to be more rigid, then examining stepping behavior would be one way to see if rigidity is necessary for random steps. Another experiment could use FRET (Forster Resonance Energy Transfer) and fluorophores on the microtubule and foot domain to track how the distance between the two regions evolves with time. This could provide information about the average distance between the MTBD and MT, which would validate this work's finding that the MTBD mostly hovers. More importantly, FRET data could be fit to models to predict the amount of diffusion the foot domain undergoes over the course of a step. Significant diffusion would indicate that diffusion may be very important for the step. Experiments with both feet labeled could get similarly good information.\\

\textbf{Talk to Dr. Hsu about this sort of thing...what experiments could be used to validate the model?}

If the model were validated by FRET and rigidity mutation studies, then there are many other interesting things which could be found from it. First, the amount of work done by the motor could be found by inducing an artificial drag force pulling the protein's motor domains against its direction of travel. This force could be integrated over dynein's trajectory to find the work the model exerted on its artificial cargo. This could be used to estimate the efficiency of the motor. Another interesting study would be to add binding sites to the model, only allowing it to bind at $\alpha-\beta$ tubulin dimerization sites, like real dynein. This would mandate re-fitting the binding constants to the new environment. It would be interesting to know if this model behaves more, or less dynein-like than the original. This would help answer the question of whether dynein searches for a binding site on the microtubule, or if it is naturally tuned to bind at the right site.\\

Another very interesting simulation which could be run could help answer the open question of why kinesin and dynein, though using similar mechanisms, produce such different steps. Kinesin, unlike dynein, conducts all of its chemistry directly on its foot. This translates to effectively having two fewer joints than dynein. Kinesin's stroke is believed to involves a similar foot unbinding, kicking forward, rebinding, then lurching the motor forward mechanism. The dynein model could be used to construct a very rough model of kinesin by shrinking the tail linkers and increasing the motor domain spring constant $c_m$ high enough to simulate a rigid hinge. This model could then be reduced to the size of kinesin, given the proper equilibrium angles, and simulated with Brownian dynamics. If this new model even roughly manages to mimic experimental kinesin stepping,that would be fascinating. This result would show that the differences betwen kinesin and dynein can be explained exclusively through the values of spring constants $c_t$, $c_m$, $c_b$, lengths $L_s$ and $L_t$, equilibrium angles and un/binding constants. This would mean the differences between the two motors are primarily due to the conformational angles the motors take with the microtubule and between their own domains, not because of differences in their mechanism.\\

Next: add Big Questions to introduction, then answer them here.\\
